### 2021-10-21 text/outline/outline.tex
proof of monotonicity

We rewrite the attenuation fraction $\gamma$ in a way that makes it more amenable to theoretical analysis. We leverage the fact that $f$ integrates to unity and is even.
First,
\begin{multline}\label{thm:gamma_expression_1} \E\left[\hat{p}_i\right] = (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) + \pi \left(\int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right), \end{multline}
 and so \begin{multline}\label{thm:gamma_expression_2} 1 - \E\left[\hat{p}_i\right] = (1 - \pi) + \pi - \E[\hat{p}_i]  = (1-\pi) \left(1 - \int_{c - \beta_0^g}^\infty f \right)  + \pi \left(1 - \int_{c - \beta^g_0 - \beta^g_1}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right).
\end{multline}
Next,
\begin{equation}\label{thm:gamma_expression_3}
\omega = \int_{c - \beta^g_1 - \beta^g_0}^\infty f,\end{equation} and so
\begin{multline}\label{thm:gamma_expression_4}
\omega - \E[\hat{p}_i]  = \left( \int_{c - \beta^g_1 - \beta^g_0}^\infty f \right) - (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) - \pi \left( \int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left(\int_{c - \beta^g_0 - \beta^g_1 }^\infty f \right) - (1- \pi) \left(\int_{c - \beta^g_0}^\infty f \right) \\ =  (1 - \pi)\left(\int_{-\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right).
\end{multline}
Combining (\ref{thm:gamma_expression_1}, \ref{thm:gamma_expression_2}, \ref{thm:gamma_expression_3}, \ref{thm:gamma_expression_4}), we find that
\begin{multline}\label{gamma_alternative}
\gamma(\beta^g_1, c, \pi) = \frac{\pi(\omega - \E[\hat{p}_i])}{\E[\hat{p}_i](1 - \E[\hat{p}_i])} \\ = \frac{\pi \left[ (1 - \pi) \left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) \right]}{\left[(1-\pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[(1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
As a corollary, when $\pi = 1/2$,
\begin{multline}\label{gamma_alternative_pi_half}
\gamma(\beta^g_1, c, 1/2)  \\ = \frac{\left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - \left( \int_{-\infty}^{ \beta_0^g - c} f \right) }{ \left[ \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[\left( \int_{-\infty}^{c - \beta^g_0} f \right) + \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
Recalling the definitions of $g$ (\ref{def_g}) and $h$ (\ref{def_h}), we can write $\gamma$ as
$$ \gamma(\beta^g_1, c, \pi) = \frac{\pi g(\beta^g_1, c, \pi)}{h(\beta^g_1, c,\pi)}.$$

\subsubsection{Derivatives of  $g$ and $h$ in $c$}

We compute the derivatives of $g$ and $h$ in $c$, which we will need to prove subsequent results. First, by FTC and the evenness of $f$, we have that
\begin{multline}\label{dg_dc}
D_2 g(\beta^g_1, c, \pi) = -(1-\pi)f( \beta^g_0 + \beta^g_1 - c ) + (1-\pi) f(\beta^g_0 - c) \\ = (1-\pi) f(c - \beta^g_0) - (1-\pi)f(c - \beta^g_0 - \beta^g_1).
\end{multline}
Second, we have that
\begin{multline}\label{dh_dc}
D_2 h(\beta^g_1, c, \pi) \\ = -[(1-\pi)f(\beta^g_0 - c) + \pi f( \beta^g_0 + \beta^g_1 - c )]\left[(1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right] \\ + [(1-\pi) f(c - \beta^g_0) +  \pi f(c - \beta^g_0 - \beta^g_1)] \left[(1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \\ = \left[ (1-\pi) f(c - \beta^g_0) +  \pi f(c - \beta^g_0 - \beta^g_1) \right] \cdot \\ \bigg[ (1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \\ - (1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) - \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \bigg].
\end{multline}

@@

\subsubsection{Bayes-optimal decision boundary as a critical value of $\gamma$}
Let $c_\textrm{bayes} = \beta^g_0 + (1/2)\beta^g_1.$ We show that $c = c_\textrm{bayes}$ is a critical value of $\gamma$ for $\pi = 1/2$ and given $\beta^g_1$, i.e, $$D_2 \gamma (\beta^g_1, c_\textrm{bayes}, 1/2) = 0.$$ By the quotient rule,
\begin{multline}\label{quotient_rule}
D_2\gamma(\beta^g_1, c, 1/2) \\ = \frac{(1/2) D_2g(\beta^g_1, c, 1/2) h(\beta^g_1, c, 1/2) - (1/2) g(\beta^g_1, c, 1/2) D_2 h(\beta^g_1, c, 1/2)}{[h(\beta^g_1, c, \pi)]^2} \\ = \frac{\left[4(1/2) D_2g(\beta^g_1, c, 1/2)\right] h(\beta^g_1, c, 1/2) - (1/2) g(\beta^g_1, c, 1/2) \left[4 D_2 h(\beta^g_1, c, 1/2)\right]}{[2h(\beta^g_1, c, \pi)]^2},
\end{multline}
where the second equality multiplies both numerator and denominator by $4$. We have by (\ref{dg_dc}) that
\begin{multline}\label{dg_dc_bayes}
4 \cdot (1/2) \cdot D_2 g(\beta^g_1, c_\textrm{bayes}, 1/2)  = f( \beta^g_1/2) - f( -\beta^g_1/2) \\ = f(\beta^g_1/2) - f(\beta^g_1/2) = 0.
\end{multline}
Next, we have by (\ref{dh_dc}) that
\begin{multline}\label{dh_dc_bayes}
4 \cdot D_2 h(\beta^g_1, c_\textrm{bayes}, \pi) = [f( \beta^g_1/2) + f( -\beta^g_1/2)] \cdot \\ \left[  \int_{-\infty}^{-\beta^g_1/2} f + \int_{-\infty}^{\beta^g_1/2} f - \int_{-\infty}^{\beta^g_1/2} f - \int_{-\infty}^{-\beta^g_1/2} f \right] = 0.
\end{multline}
Plugging in (\ref{dh_dc_bayes}) and (\ref{dg_dc_bayes}) to (\ref{quotient_rule}), we find that 
$$D_2(\beta^g_1, c_\textrm{bayes}, 1/2) = 0.$$

% $$g'(\cdot, c) = - f( \beta^g_0 + \beta^g_1 - c ) + f(\beta^g_0 - c).$$ Second, 
% \begin{multline*}
% h'(\cdot, c) = -[f(\beta^g_0 - c)  + f( \beta^g_0 + \beta^g_1 - c )]  \left[\left( \int_{-\infty}^{c - \beta^g_0} f \right) + \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right] \\ +[ f(c - \beta^g_0) + f(c - \beta^g_0 - \beta^g_1) ] \left[ \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right].
% \end{multline*}
% Evaluating $g'(\cdot, c)$ and $h'(\cdot, c)$ at $c = c_\textrm{bayes} $, we find that
% $$g'(\beta^g_0 + (1/2) \beta^g_1) = -f(\beta^g_1/2) + f(- \beta^g_1/2) = -f(\beta^g_1/2) + f(\beta^g_1/2) = 0,$$ where the second equality follows from the evenness of $f$. Similarly, 
% \begin{multline*}
% h'(\beta^g_0 + (1/2) \beta^g_1) = - \left[ f( -\beta^g_1/2) + f( \beta^g_1/2 ) \right] \left[ \int_{-\infty}^{ \beta^g_1/2} f + \int_{-\infty}^{ -\beta^g_1/2} f \right] + \\ \left[ f( \beta^g_1/2) + f( -\beta^g_1/2 ) \right] \left[ \int_{-\infty}^{ -\beta^g_1/2} f + \int_{-\infty}^{ \beta^g_1/2 f} \right] = 0.
% \end{multline*}
% We conclude that
% $$ \frac{\partial \gamma(\beta^g_0, \beta^g_1, c, 1/2)}{ \partial c} \vline_{[c = c_\textrm{bayes}]} = \frac{0\cdot h(\cdot, c_\textrm{bayes}) - g(\cdot, c_\textrm{bayes}) \cdot 0}{ h(\cdot, c_\textrm{bayes})^2} = 0.$$ Finally, because asymptotic bias $b$ can be expressed in terms of $\gamma$ as $$b(\beta^g_0. \beta^g_1, c, \pi) = \beta^m_1 \left[ 1 - \gamma(\beta^g_0, \beta^g_1, c, \pi) \right],$$ it follows that $c = c_\textrm{bayes}$ is a critical value of $b$ for $\pi = 1/2$ and fixed $(\beta^g_0, \beta^g_1)$.

% \subsubsection{Limit in $\beta^g_1$}

% We compute the limit of $\gamma(\beta^g_0, \beta^g_1, c, 1/2)$ in $\beta^g_1.$ We have that

% \begin{multline*}
 %\lim_{\beta^g_1 \to \infty } \gamma(\beta^g_0, \beta^g_1, c, 1/2) = \frac{ 1 - \int_{-\infty}^{\beta^g_0 - c } f}{\left[ 1 + \int_{-\infty}^{ \beta^g_0 - c} f \right] \left[\int_{-\infty}^{ c - \beta^g_0} f \right]} \\ = \frac{\int_{-\infty}^{c - \beta^g_0} f }{ \left[1 + \int_{-\infty}^{ \beta^g_0 - c} f \right] \left[\int_{-\infty}^{ c - \beta^g_0} f \right]} = \frac{1}{1 + \int_{-\infty}^{\beta^g_0 - c} f} < 1.
% \end{multline*}

% Similarly,
% \begin{multline*}
% \lim_{\beta^g_1 \to -\infty} \gamma(\beta^g_0, \beta^g_1, c, 1/2) = \frac{ -\int_{-\infty}^{\beta^g_0 - c} f }{\left[ \int_{-\infty}^{\beta^g_0 - c} f \right] \left[ \int_{-\infty}^{c - \beta^g_0} f + 1 \right]} = \frac{-1}{1 + \int_{-\infty}^{c - \beta^g_0} f} > -1.
% \end{multline*}

% \subsubsection{Monotonicity in $\beta^g_1$}
% We prove that $\gamma$ is monotonic in $\beta_1^g$ for given $(\beta^g_0, c)$ and $\pi = 1/2$. Recall that
% $$\gamma(\beta^g_0, \beta^g_1, c, 1/2) = \frac{ g(\beta^g_1, c) }{ h(\beta^g_1, c)}.$$ By the quotient rule,
% $$D_2 \gamma (\beta^g_0, \beta^g_1, c, 1/2) = \frac{D_1 g( \beta^g_1, c) h(\beta^g_1, c) - g(\beta^1_g, c) D_1 h(\beta^g_1, c) }{ [ h(\beta^g_1, c)^2]}.$$ The derivative $D_1 g(\beta^g_1, c)$ of $g$ is 
% $$D_1 g(\beta^g_1, c) = f( \beta^g_0 + \beta^g_1 - c ).$$

>>>>

We rewrite the attenuation fraction $\gamma$ in a way that makes it more amenable to theoretical analysis. We leverage the fact that $f$ integrates to unity and is even.
First,
\begin{multline}\label{thm:gamma_expression_1} \E\left[\hat{p}_i\right] = (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) + \pi \left(\int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right), \end{multline}
 and so \begin{multline}\label{thm:gamma_expression_2} 1 - \E\left[\hat{p}_i\right] = (1 - \pi) + \pi - \E[\hat{p}_i]  = (1-\pi) \left(1 - \int_{c - \beta_0^g}^\infty f \right)  + \pi \left(1 - \int_{c - \beta^g_0 - \beta^g_1}^\infty f \right) \\ = (1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right).
\end{multline}
Next,
\begin{equation}\label{thm:gamma_expression_3}
\omega = \int_{c - \beta^g_1 - \beta^g_0}^\infty f,\end{equation} and so
\begin{multline}\label{thm:gamma_expression_4}
\omega - \E[\hat{p}_i]  = \left( \int_{c - \beta^g_1 - \beta^g_0}^\infty f \right) - (1 - \pi) \left( \int_{c - \beta^g_0}^\infty f \right) - \pi \left( \int_{c - \beta_0^g - \beta_1^g}^\infty f \right) \\ = (1 - \pi) \left(\int_{c - \beta^g_0 - \beta^g_1 }^\infty f \right) - (1- \pi) \left(\int_{c - \beta^g_0}^\infty f \right) \\ =  (1 - \pi)\left(\int_{-\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right).
\end{multline}
Combining (\ref{thm:gamma_expression_1}, \ref{thm:gamma_expression_2}, \ref{thm:gamma_expression_3}, \ref{thm:gamma_expression_4}), we find that
\begin{multline}\label{gamma_alternative}
\gamma(\beta^g_1, c, \pi) = \frac{\pi(\omega - \E[\hat{p}_i])}{\E[\hat{p}_i](1 - \E[\hat{p}_i])} \\ = \frac{\pi \left[ (1 - \pi) \left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - (1 - \pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) \right]}{\left[(1-\pi) \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \pi \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[(1 - \pi) \left( \int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left( \int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
As a corollary, when $\pi = 1/2$,
\begin{multline}\label{gamma_alternative_pi_half}
\gamma(\beta^g_1, c, 1/2)  \\ = \frac{\left( \int_{ -\infty}^{\beta_0^g + \beta_1^g - c} f \right) - \left( \int_{-\infty}^{ \beta_0^g - c} f \right)}{\left[ \left( \int_{-\infty}^{ \beta_0^g - c} f \right) + \left( \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \left[\left( \int_{-\infty}^{c - \beta^g_0} f \right) + \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right]}.
\end{multline}
Recalling the definitions of $g$ (\ref{def_g}) and $h$ (\ref{def_h}), we can write $\gamma$ as
$$ \gamma(\beta^g_1, c, \pi) = \frac{\pi g(\beta^g_1, c, \pi)}{h(\beta^g_1, c,\pi)}.$$
The special case (\ref{gamma_alternative_pi_half}) is identical to
\begin{equation}\label{gamma_alt2_pi_half}
\gamma(\beta^g_1, c, 1/2) = \frac{(4)(1/2)g(\beta^g_1, c, 1/2)}{4 h(\beta^g_1, c, 1/2)} = \frac{2 g(\beta^g_1, c, 1/2)}{4h(\beta^g_1, c, 1/2)},
\end{equation}
i.e., the numerator and denominator of  (\ref{gamma_alt2_pi_half}) coincide with those of (\ref{gamma_alternative_pi_half}).

\subsubsection{Derivatives of  $g$ and $h$ in $c$}
We compute the derivatives of $g$ and $h$ in $c$, which we will need to prove subsequent results. First, by FTC and the evenness of $f$, we have that
\begin{multline}\label{dg_dc}
D_2 g(\beta^g_1, c, \pi) = -(1-\pi)f( \beta^g_0 + \beta^g_1 - c ) + (1-\pi) f(\beta^g_0 - c) \\ = (1-\pi) f(c - \beta^g_0) - (1-\pi)f(c - \beta^g_0 - \beta^g_1).
\end{multline}
Second, we have that
\begin{multline}\label{dh_dc}
D_2 h(\beta^g_1, c, \pi) \\ = -[(1-\pi)f(\beta^g_0 - c) + \pi f( \beta^g_0 + \beta^g_1 - c )]\left[(1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) + \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \right] \\ + [(1-\pi) f(c - \beta^g_0) +  \pi f(c - \beta^g_0 - \beta^g_1)] \left[(1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \right] \\ = \left[ (1-\pi) f(c - \beta^g_0) +  \pi f(c - \beta^g_0 - \beta^g_1) \right] \cdot \\ \bigg[ (1-\pi)\left( \int_{-\infty}^{\beta_0^g - c} f \right) + \pi \left(\int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f \right) \\ - (1-\pi)\left(\int_{-\infty}^{c - \beta^g_0} f \right) - \pi \left(\int_{-\infty}^{c - \beta_0^g - \beta_1^g} f \right) \bigg].
\end{multline}

@@

\subsubsection{Bayes-optimal decision boundary as a critical value of $\gamma$}
Let $c_\textrm{bayes} = \beta^g_0 + (1/2)\beta^g_1.$ We show that $c = c_\textrm{bayes}$ is a critical value of $\gamma$ for $\pi = 1/2$ and given $\beta^g_1$, i.e, $$D_2 \gamma (\beta^g_1, c_\textrm{bayes}, 1/2) = 0.$$ By the quotient rule,
\begin{multline}\label{quotient_rule}
D_2\gamma(\beta^g_1, c, 1/2) \\ = \frac{(1/2) D_2g(\beta^g_1, c, 1/2) h(\beta^g_1, c, 1/2) - (1/2) g(\beta^g_1, c, 1/2) D_2 h(\beta^g_1, c, 1/2)}{[h(\beta^g_1, c, \pi)]^2} \\ = \frac{\left[4(1/2) D_2g(\beta^g_1, c, 1/2)\right] h(\beta^g_1, c, 1/2) - (1/2) g(\beta^g_1, c, 1/2) \left[4 D_2 h(\beta^g_1, c, 1/2)\right]}{[2h(\beta^g_1, c, \pi)]^2},
\end{multline}
where the second equality multiplies both numerator and denominator by $4$. We have by (\ref{dg_dc}) that
\begin{multline}\label{dg_dc_bayes}
4 \cdot (1/2) \cdot D_2 g(\beta^g_1, c_\textrm{bayes}, 1/2)  = f( \beta^g_1/2) - f( -\beta^g_1/2) \\ = f(\beta^g_1/2) - f(\beta^g_1/2) = 0.
\end{multline}
Next, we have by (\ref{dh_dc}) that
\begin{multline}\label{dh_dc_bayes}
4 \cdot D_2 h(\beta^g_1, c_\textrm{bayes}, \pi) = [f( \beta^g_1/2) + f( -\beta^g_1/2)] \cdot \\ \left[  \int_{-\infty}^{-\beta^g_1/2} f + \int_{-\infty}^{\beta^g_1/2} f - \int_{-\infty}^{\beta^g_1/2} f - \int_{-\infty}^{-\beta^g_1/2} f \right] = 0.
\end{multline}
Plugging in (\ref{dh_dc_bayes}) and (\ref{dg_dc_bayes}) to (\ref{quotient_rule}), we find that 
$$D_2(\beta^g_1, c_\textrm{bayes}, 1/2) = 0.$$ It follows that $c_\textrm{bayes}$ is a critical value of the bias function $b$.

\subsubsection{Limit in $\beta^g_1$}

We compute the limit of $\gamma$ in $\beta^g_1$ given $\pi = 1/2$.  First,
\begin{multline*}
 \lim_{\beta^g_1 \to \infty} \gamma(\beta^g_1, c, 1/2) = \frac{ 1 - \int_{-\infty}^{\beta^g_0 - c} f}{\left[ 1 + \int_{-\infty}^{ \beta^g_0 - c} f \right] \left[\int_{-\infty}^{ c - \beta^g_0} f \right]} \\ = \frac{\int_{-\infty}^{c - \beta^g_0} f }{ \left[1 + \int_{-\infty}^{ \beta^g_0 - c} f \right] \left[\int_{-\infty}^{ c - \beta^g_0} f \right]} = \frac{1}{1 + \int_{-\infty}^{\beta^g_0 - c} f} < 1.
\end{multline*}
Similarly,
\begin{multline*}
\lim_{\beta^g_1 \to -\infty} \gamma(\beta^g_1, c, 1/2) = \frac{ -\int_{-\infty}^{\beta^g_0 - c} f }{\left[ \int_{-\infty}^{\beta^g_0 - c} f \right] \left[ \int_{-\infty}^{c - \beta^g_0} f + 1 \right]} = \frac{-1}{1 + \int_{-\infty}^{c - \beta^g_0} f} > -1.
\end{multline*}

\subsubsection{Monotonicity in $\beta^g_1$}

We show that $\gamma$ is monotonically increasing in $\beta_1^g$ for $\pi = 1/2$. First, we compute the derivative of (\ref{gamma_alt2_pi_half}) with respect to $\beta^g_1$. The quotient rule implies that
\begin{multline}\label{d_gamma_d_beta}
D_1 \gamma(\beta^g_1, c, 1/2) \\ = \frac{D_1[2g(\beta^g_1, c, 1/2)] 4h(\beta^g_1, c, 1/2) - 2g(\beta^g_1, c, 1/2)D_1[4h(\beta^g_1, c, 1/2)]}{[4h(\beta^g_1, c, 1/2)]^2}.
\end{multline}
First,
$$\textcolor{violet}{D_1[2g(\beta^g_1, c, 1/2)] = f(\beta^g_0 + \beta^g_1 - c)}.$$
Next,
\begin{multline*}
\textcolor{teal}{D_1[4h(\beta^g_1, c, 1/2)] = f(\beta^g_0 + \beta^g_1 - c) \left[\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g) \right]} \\ \textcolor{teal}{- f(\beta^g_0 + \beta^g_1 - c) \left[\Phi(\beta_0^g - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right]}.\end{multline*}
Recall that
$$\textcolor{blue}{2g(\beta^g_1,c,1/2) = \Phi(\beta^g_0 + \beta^g_1 - c) - \Phi(\beta^g_0 - c)}.$$
and
$$\textcolor{red}{4h(\beta^g_1, c, 1/2) = \left[ \Phi(\beta^g_0 - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right] \left[\Phi(c - \beta^g_0) + \Phi( c - \beta^g_0 - \beta^g_1) \right]}.$$
To show that $\gamma$ is monotonically increasing in $\beta^g_1$, it is sufficient to show that (\ref{d_gamma_d_beta}) is nonnegative, i.e.
\begin{equation}\label{thm:gamma_monotonic_1}
\textcolor{violet}{D_1[2g(\beta^g_1, c, 1/2)]}\textcolor{red}{4h(\beta^g_1, c, 1/2)} \geq \textcolor{blue}{2g(\beta^g_1, c, 1/2)}\textcolor{teal}{D_1[4h(\beta^g_1, c, 1/2)]}.
\end{equation}
The product $\textcolor{violet}{D_1[2g(\beta^g_1, c, 1/2)]}\textcolor{red}{4h(\beta^g_1, c, 1/2)}$ is
\begin{multline}\label{g_prime_times_h}
\textcolor{violet}{D_1[2g(\beta^g_1, c, 1/2)]}\textcolor{red}{4h(\beta^g_1, c, 1/2)} \\ = \textcolor{violet}{f(\beta^g_0 + \beta^g_1 - c)}\textcolor{red}{\left[ \Phi(\beta_0^g - c ) + \Phi(\beta^g_0 + \beta^g_1 - c)\right]\left[\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g) \right]}.
\end{multline} 
Next, the product $\textcolor{blue}{2g(\beta^g_1, c, 1/2)}\textcolor{teal}{D_1[4h(\beta^g_1, c, 1/2)]}$ is
\begin{multline}\label{g_times_h_prime}
\textcolor{blue}{2g(\beta^g_1, c, 1/2)}\textcolor{teal}{D_1[4h(\beta^g_1, c, 1/2)]} \\ = \textcolor{teal}{f(\beta^g_0 + \beta^g_1 - c)}\textcolor{blue}{\left[\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c)\right]}\textcolor{teal}{\left[\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g) \right]} \\ - \textcolor{teal}{f(\beta^g_0 + \beta^g_1 - c)}\textcolor{teal}{\left[\Phi(\beta_0^g - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right]} \textcolor{blue}{\left[\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c)\right]}.
\end{multline}
Divide both sides by $f(\beta^g_0 - \beta^g_1 - c) > 0$. Then, add
$$\textcolor{teal}{\left[\Phi(\beta_0^g - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right]}\textcolor{blue}{\left[\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c)\right]}.$$ The left-hand side becomes
\begin{multline*}
\textcolor{red}{\left[ \Phi(\beta_0^g - c ) + \Phi(\beta^g_0 + \beta^g_1 - c)\right]\left[\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g) \right]} \\ +\textcolor{teal}{\left[\Phi(\beta_0^g - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right]}\textcolor{blue}{\left[\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c)\right]} \\ = \left[\Phi(\beta^g_0 - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right] \\ \cdot \left[\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g) + \Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c) \right].
\end{multline*}
Meanwhile, the right-hand side becomes
$$\left[\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c)\right]\left[\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g) \right].$$
Therefore, we want to demonstrate that
\begin{multline}\label{basic_ineq}
\left[\Phi(\beta^g_0 - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right] \\ \cdot \left[\textcolor{brown}{\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c)} + \textcolor{olive}{\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g)} \right] \\ \geq \left[\textcolor{brown}{\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c)}\right]\left[\textcolor{olive}{\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g)}\right].
\end{multline}
(We changed the color scheme to highlight like terms.)
We take cases on the sign on $\beta^g_1$ to prove this inequality.
\\ \\ \noindent
\textbf{Case 1}: $\beta^1_g < 0$. Then $ \beta^g_1 + (\beta^g - c) < (\beta^g_0 - c),$ implying $\Phi(\beta^g_0 + \beta^g_1 - c) < \Phi(\beta^g_0 - c),$ or $[\Phi(\beta^g_0 + \beta^g_1 - c) - \Phi(\beta^g_0 - c)] < 0.$ Moreover, the quantity $[\Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g)]$ is positive. Thus, the right-hand side of (\ref{basic_ineq}) is negative.

Turning our attention of the left-hand side, we have that
\begin{multline*}
\Phi(\beta^g_0 + \beta^g_1 - c) + \Phi( c - \beta^g_0 - \beta^g_1) = \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f + \int_{-\infty}^{c - \beta^g_0 - \beta^g_1} f \\ = \int_{-\infty}^{ \beta^g_0 + \beta^g_1 - c} f  + \int_{\beta^g_0 + \beta^g_1 - c}^\infty f = 1.
\end{multline*}
Additionally, $\Phi(\beta^g_0 - c) < 1,$ and $ \Phi(c - \beta^g_0) > 0$. Combining these expressions, we find that
$$ \left[\Phi(\beta_0^g + \beta_1^g - c) - \Phi(\beta_0^g - c) + \Phi(c - \beta^g_0) + \Phi(c - \beta_0^g - \beta_1^g) \right] > 0. $$ Because $\left[\Phi(\beta^g_0 - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \right] > 0,$ it follows that the entire left-hand side of (\ref{basic_ineq}) is positive.
\\ \\ \noindent
\textbf{Case 2}: $\beta^1_g \geq 0.$  We show that the first term on the LHS of (\ref{basic_ineq}) is greater than the first term on the RHS, and likewise that the second term on the LHS is greater than the second term on the RHS. First,
$$ \Phi(\beta^g_0 - c) \geq - \Phi(\beta^g_0 - c),$$ implying
$$ \Phi(\beta^g_0 - c) + \Phi(\beta^g_0 + \beta^g_1 - c) \geq \Phi(\beta^g_0 - \beta^g_1 - c) - \Phi(\beta^g_0 - c).$$
Second, $\beta^g_1 \geq 0$ implies that $\beta^g_1 + \beta^g_0 - c \geq \beta^g_0 - c,$ and so $$\Phi(\beta^g_1 + \beta^g_0 - c) - \Phi(\beta^g_0 - c) \geq 0.$$ Finally, 
$$ \Phi(\beta^g_1 + \beta^g_0 - c) - \Phi(\beta^g_0 - c) + \Phi(c - \beta^g_0) + \Phi(c - \beta^g_0 - \beta^g_1) \geq \Phi(c - \beta^g_0) + \Phi(c - \beta^g_0 - \beta^g_1).$$
Therefore, the inequality (\ref{basic_ineq}) holds.

\subsubsection{Attenuation bias}

For given $(\beta^g_0, \beta^g_1)$,
